Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-06 draft.tex
abstract updates and title options

\def\Title{Creating More Meaningful Explanations for Audio Deepfake Detection}
\def\Subtitle{}

@@

	sample that can be heard by the human ear, perceptible features. We use this classifier as a
	surrogate model to produce explanations using the LIME method, with the hope of introducing a
	kind of explainability into this area that has the potential to be understood by a wider range
	of people and not only people who are already familiar with the field, in addition to
	introducing two metrics in order to evaluate the contributions of the features to the average
	local explanation through aggregation, with the goal of making a conclusion about the
	potential usefulness of explanations generated using this method to more general audience.
	Experiments were performed using the In-the-Wild dataset, a dataset created with a focus on
	testing generalization of previous methods of synthetic audio detection. Several of the
	surrogate models demonstrated strong performance on the dataset, even in comparison to
	previous methods. However, the explanations generated by this method do not seem to offer much
	potential for useful interpretation using the perceptible features, based on an evaluation of
	aggregated local explanations using the proposed metrics, as the imperceptible features have a
	much larger influence on the classification result. We believe, however, that the proposed
	method offers a promising basis for future research into explanations using perceptible
	features.

>>>>

\def\Title{
	Creating More Meaningful Explanations of Audio Deepfake Detection
	\newline\newline
	Explaining Audio Deepfake Detection with Perceptible Features and LIME
	\newline\newline
	Understandable Explanations of Synthetic Voice Detection with Perceptible Features and LIME
}
\def\Subtitle{}

@@

	sample that can be heard by the human ear, perceptible features, that stitches multiple
	subnetworks together in order to evaluate many differently shaped input features in a singular
	model. We then use part of this classifier as a surrogate model to produce explanations using
	the LIME method, with the hope of introducing a kind of explanation into this area that has
	the potential to be understood by a wider range of people and not only people who are already
	familiar with the field. In order to evaluate the contributions of the features to the average
	local explanation, we also introduce two metrics for aggregate evaluations of many local
	explanations, with the goal of making a robust and well justified conclusion about the
	potential usefulness of explanations generated using this method. Experiments were performed
	using the In-the-Wild dataset, a dataset created with a focus on testing generalization of
	previous methods of synthetic audio detection. Several of the surrogate models demonstrated
	strong performance on the dataset, even in comparison to previous methods. However, the
	explanations generated by this method do not seem to offer much potential for useful
	interpretation using the perceptible features, based on an evaluation of aggregated local
	explanations using the proposed metrics, as the imperceptible features have a much larger
	influence on the classification result and only some of the perceptible features had a
	positive influence on the classification correctness. We believe, however, that the proposed
	method offers a promising basis for future research on creating more useful explanations using
	such feature combinations.
